Efficient pedigree recording for fast population genetics simulation

### 2017-12-28 forwards_paper.tex
clarify RAM use discussion

The peak RAM use in gigabytes (GB) is shown for the simulations with selection in Figure~\ref{sfig:ramsel} aand for the
simulations without selection in Figure~\ref{sfig:ramnosel}.  The general picture is that pedigree tracking requires
more RAM.  With \fwdpy{}/\fwdpp{}, the reason for this behavior is clear.  When pedigree tracking, a non-recombinant
individual still requires one new edge and two new nodes to be allocated.  Without pedigree tracking, no new memory is
allocated for such an offspring.  Thus, pedigree tracking accumulates a large amount of data in RAM until
simplification.  This extra RAM consumption is the trade off for reduced run times and the degree of extram RAM needed
can be reduced by simplifying more often.  The simulations where we run the simplification step in a separate thread
require even more RAM (dashed line in Figure \ref{sfig:ramsel}) because up to four epochs of unsimplified data are
stored in RAM.

\krt{I've avoided getting into how this much RAM means parallelization is required to make more progress.}

>>>>

The peak RAM use in gigabytes (GB) is shown for the simulations with selection in Figure~\ref{sfig:ramsel} aand for the
simulations without selection in Figure~\ref{sfig:ramnosel}.  For our parameters, which involved simplifying every
$10^3$ generations,  pedigree tracking requires more RAM.  With \fwdpy{}/\fwdpp{}, the reason for the extran RAM use is clear.  When pedigree tracking, a non-recombinant
individual still requires one new edge and two new nodes to be allocated.  Without pedigree tracking, no new memory is
allocated for such an offspring.  Thus, pedigree tracking accumulates a large amount of data in RAM until
simplification.  This extra RAM consumption is the trade off for reduced run times and the degree of extram RAM needed
can be reduced by simplifying more often.  The simulations where we run the simplification step in a separate thread
require even more RAM (dashed line in Figure \ref{sfig:ramsel}) because up to four epochs of unsimplified data are
stored in RAM.  In practice, the RAM consumption can be minimized by simplifying more often.

%% \krt{I've avoided getting into how this much RAM means parallelization is required to make more progress.}
